Compiling refinement types to dependent types

### 2020-07-03 tex/paper.tex
Fix duplicate labels
Use \triangleq instead of \coloneqq

\documentclass[a4paper]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage{amsmath,amsfonts}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{ottalt}
\usepackage{subcaption}

@@

For the example oracle being an SMT solver and the syntax of terms also including mathematics, $[|\ |]$ might be defined as
\begin{equation}
\begin{aligned}
  & [| \emptyset |]                                         && \coloneqq \top																						 \\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] && \coloneqq [| \nonterm G |] \land [| \{x/v\} \nonterm r |] \\
  & [| \nonterm r_1 \land \nonterm r_2 |]                   && \coloneqq [| \nonterm r_1 |] \land [| \nonterm r_2 |]		 \\
  & \cdots TODO
\end{aligned}
\end{equation}

@@

\begin{figure}[ht]
  \footnotesize
  \drules[CT]{$\nonterm G \vdash \nonterm{ec}_1 : \nonterm{ec}_2$}{core typing}{Sort,Var,Weaken,Form,App,Abs,Conv}
  \caption{Core language typing rules}
  \label{fig:surface_typing}
\end{figure}

@@

\begin{itemize}
  \item Non-dependent function type:
  \[
    \tau_1 \rightarrow \tau_2 \coloneqq \Pi x : \tau_1. \tau_2,
  \]
  where $\tau_2$ does not have $x$ free.
  \item Dependent pair type, or $\Sigma$-type, with the first component being a value $x$ of type $\tau$ and the second component being of type $P x$:
  \[
    \{ x : \tau\ **\ P x \} \coloneqq \Pi \alpha : \star. (\Pi x : \tau. P x \rightarrow \alpha) \rightarrow \alpha.
  \]
  \item Accessing the first and second component of the dependent pair:
  \[
    \text{fst} \coloneqq TODO,
  \]
  \[
    \text{snd} \coloneqq TODO.
  \]
  \item Non-dependent pair type:
  \[
    (\tau_1, \tau_2) \coloneqq \{ x : \tau_1\ **\ (\lambda \_ : \tau_1. \tau_2) x \}.
  \]
\end{itemize}

@@

We translate the surface language types and terms using the $\mu_\tau$ and $\mu_\varepsilon$ functions respectively.
$\mu_\tau$ is defined as follows:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{tS}_1) \rightarrow \nonterm{tS}_2)  && \coloneqq \Pi x : \mu_\tau(\nonterm{tS}_1). \mu_\tau(\nonterm{tS}_2)  \\
  & \mu_\tau( \{ v : \nonterm{tS} | \nonterm{r} \})             && \coloneqq \{ v : \mu_\tau(\nonterm{tS})\ **\ \mu_\tau(\nonterm r) \}  \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \coloneqq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))          \\
  & \mu_\tau( \nonterm{eS} )                                    && \coloneqq \mu_\varepsilon(\nonterm{eS}) = \text{True}                 \\
  & \mu_\tau(B)                                                 && \coloneqq B                                                           \\
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements (which are $\text{Bool}$-typed terms) are translated to propositions stating that the corresponding term is equal to $\text{True}$,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}

>>>>

\documentclass[a4paper]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{ottalt}
\usepackage{subcaption}

@@

For the example oracle being an SMT solver and the syntax of terms also including mathematics, $[|\ |]$ might be defined as
\begin{equation}
\begin{aligned}
  & [| \emptyset |]                                         && \triangleq \top																						 \\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] && \triangleq [| \nonterm G |] \land [| \{x/v\} \nonterm r |] \\
  & [| \nonterm r_1 \land \nonterm r_2 |]                   && \triangleq [| \nonterm r_1 |] \land [| \nonterm r_2 |]		 \\
  & \cdots TODO
\end{aligned}
\end{equation}

@@

\begin{figure}[ht]
  \footnotesize
  \drules[CT]{$\nonterm G \vdash \nonterm{ec}_1 : \nonterm{ec}_2$}{core typing}{Sort,Var,Weaken,Form,App,Abs,Conv}
  \caption{Core language typing rules}
  \label{fig:core_typing}
\end{figure}

@@

\begin{itemize}
  \item Non-dependent function type:
  \[
    \tau_1 \rightarrow \tau_2 \triangleq \Pi x : \tau_1. \tau_2,
  \]
  where $\tau_2$ does not have $x$ free.
  \item Dependent pair type, or $\Sigma$-type, with the first component being a value $x$ of type $\tau$ and the second component being of type $P x$:
  \[
    \{ x : \tau\ **\ P x \} \triangleq \Pi \alpha : \star. (\Pi x : \tau. P x \rightarrow \alpha) \rightarrow \alpha.
  \]
  \item Accessing the first and second component of the dependent pair:
  \[
    \text{fst} \triangleq TODO,
  \]
  \[
    \text{snd} \triangleq TODO.
  \]
  \item Non-dependent pair type:
  \[
    (\tau_1, \tau_2) \triangleq \{ x : \tau_1\ **\ (\lambda \_ : \tau_1. \tau_2) x \}.
  \]
\end{itemize}

@@

We translate the surface language types and terms using the $\mu_\tau$ and $\mu_\varepsilon$ functions respectively.
$\mu_\tau$ is defined as follows:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{tS}_1) \rightarrow \nonterm{tS}_2)  && \triangleq \Pi x : \mu_\tau(\nonterm{tS}_1). \mu_\tau(\nonterm{tS}_2)  \\
  & \mu_\tau( \{ v : \nonterm{tS} | \nonterm{r} \})             && \triangleq \{ v : \mu_\tau(\nonterm{tS})\ **\ \mu_\tau(\nonterm r) \}  \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \triangleq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))          \\
  & \mu_\tau( \nonterm{eS} )                                    && \triangleq \mu_\varepsilon(\nonterm{eS}) = \text{True}                 \\
  & \mu_\tau(B)                                                 && \triangleq B                                                           \\
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements (which are $\text{Bool}$-typed terms) are translated to propositions stating that the corresponding term is equal to $\text{True}$,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}
